\section*{Introduction}
\phantomsection

\textbf{SQL} stands for Structured Query Language, is a domain-specific language used in programming and designed for managing data held in a relational database management system (RDBMS), or for stream processing in a relational data stream management system. Originally based upon relational algebra and tuple relational calculus, SQL consists of a data definition language, data manipulation language, and data control language. The scope of SQL includes data insert, query, update and delete, schema creation and modification, and data access control. Although SQL is often described as, and to a great extent is, a declarative language (4GL), it also includes procedural elements.

Clauses, which are constituent components of statements and queries. (In some cases, these are optional.)
Expressions, which can produce either scalar values, or tables consisting of columns and rows of data
Predicates, which specify conditions that can be evaluated to SQL three-valued logic (3VL) (true/false/unknown) or Boolean truth values and are used to limit the effects of statements and queries, or to change program flow.
Queries, which retrieve the data based on specific criteria. This is an important element of SQL.
Statements, which may have a persistent effect on schemata and data, or may control transactions, program flow, connections, sessions, or diagnostics.
SQL statements also include the semicolon (";") statement terminator. Though not required on every platform, it is defined as a standard part of the SQL grammar.
Insignificant whitespace is generally ignored in SQL statements and queries, making it easier to format SQL code for readability.

\clearpage