\begin{thebibliography}{99999}
\phantomsection
\singlespace\normalsize

\bibitem{NaoOfficial} Aldebran Robotics, \textit{ official page}, \url{www.aldebaran.com/en}

\bibitem{doc} Aldebran Robotics, \textit{NAO Software 2.1.3 documentation}  \url{www.doc.aldebaran.com/2-1/index.html}

\bibitem{OC} OpenCV Dev Team, \textit{OpenCV 2.4.9.0 documentation}, \url{www.opencv.org/modules/refman.html}

\bibitem{Ojala} Timo Ojala, \textit{Multiresolution gray-scale and rotation invariant texture classification with local binary patterns}, 2002

\bibitem{Solem} Jan Erik Solem, \textit{Programming Computer Vision with Python}, 2012

\bibitem{FRUE} M. A. Turk and A. P. Pentland, \textit{Face Recognition Using Eigenfaces}, 1991.

\bibitem{SKK}S. Suhas, A. Kurhe, Dr.P. Khanale, \textit{Face Recognition Using Principal Component Analysis and Linear Discriminant Analysis on Holistic Approach in Facial Images Database}, Vol. 2, December 2012

\bibitem{Chellappa} W. Zhao, R. Chellappa, P. J. Phillips and A. Rosenfeld, \textit{Face recognitions literature survey'}, ACM Computing Surveys, Vol. 35, No. 4, December 2003, pp. 399–458

\bibitem{} Sukhan Lee, Hyungsuck Cho, Kwang-Joon Yoon, Jangmyung Lee, \textit{Intelligent Autonomous Systems 12}, Volume 1

\bibitem{Ismail} Shah Alam, Malaysia Shamsuddin, \textit{Face detection technique of Humanoid Robot NAO for application in robotic assistive therapy}, Center of Excellence for Humanoid Robot Bio-Sensing (HuRoBs), Univ. Teknol. MARA

\bibitem{ES1} Xavier Alameda-Pineda, Vasil Khalidov, Radu Horaud and Florence Forbes, \textit{Finding Audio-Visual Events in Informal Social Gatherings}

\bibitem{ES2}Jan Cech, Ravi Mittal, Antoine Deleforge, \textit{Active-Speaker Detection and Localization with Microphones and Cameras Embedded into a Robotic Head}, Humanoids 2013 - IEEE-RAS International Conference on Humanoid Robots, Oct 2013, Atlanta, United States. 2013

\bibitem{ES3} Xavier Alameda-Pineda, Radu Horaud, \textit{Vision-Guided Robot Hearing}, The International Journal of Robotics Research, SAGE Publications (UK and US), 2015


\end{thebibliography}
